The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-15 src/ms.tex
fix language around LTS. fixes #98
fix en dash issue

Major versions of the core package --- that is, versions that add and/or modify
functionality --- are released approximately every six months, and are then
maintained with releases that fix issues until the next major version is
released. However, every two years a major release is designated as a long-term
support (LTS) release, which continues to be maintained for up to two years
\citep{ape2}. The motivation for LTS releases is to provide longer-term stable
versions of \astropypkg that users who require a high level of stability can
make use of if they do not always need the latest features (this includes but
is not limited to telescope operations and data reduction pipelines). The v5.0
release of the core package, replacing v4.0, was designated as LTS at the end of 2021;
it will be maintained until the end of 2023.

@@

The data analysis pipeline is developed as open-source software and essentially split in two domains:
\begin{enumerate}
  \item In the low-level analysis, the properties of the recorded air-shower events
    have to be estimated from the raw data.
    The raw data consists of very short (\textasciitilde $40--100\,\mathrm{ns}$) videos recorded with the fast and
    sensitive cameras of the telescopes.
    This includes the energy, particle type and direction of origin of the particle that induced the air shower
    and the time the shower was recorded.
  \item In the higher-level analysis, these reconstructed event lists are used together with some
    characterization of the instrument response to perform the actual scientific analysis.
    This software will be delivered as CTA science tools to the future users of the Observatory.
\end{enumerate}

>>>>

Major versions of the core package --- that is, versions that add and/or modify
functionality --- are released approximately every six months, and are then
maintained with releases that fix issues until the next major version is
released. However, every two years a major release is designated as a long-term
support (LTS) release, which continues to be maintained for at least two years
\citep{ape2}. The motivation for LTS releases is to provide longer-term stable
versions of \astropypkg that users who require a high level of stability can
make use of if they do not always need the latest features (this includes but
is not limited to telescope operations and data reduction pipelines). The v5.0
release of the core package, replacing v4.0, was designated as LTS at the end of 2021;
it will be maintained until the end of 2023.

@@

The data analysis pipeline is developed as open-source software and essentially split in two domains:
\begin{enumerate}
  \item In the low-level analysis, the properties of the recorded air-shower events
    have to be estimated from the raw data.
    The raw data consists of very short ($\sim40$--$100\,\mathrm{ns}$) videos recorded with the fast and
    sensitive cameras of the telescopes.
    This includes the energy, particle type and direction of origin of the particle that induced the air shower
    and the time the shower was recorded.
  \item In the higher-level analysis, these reconstructed event lists are used together with some
    characterization of the instrument response to perform the actual scientific analysis.
    This software will be delivered as CTA science tools to the future users of the Observatory.
\end{enumerate}
